Data Preparation

### 2019-01-17 Data Preparation.Rmd

# Import Data
The datasets we use are saved as spreadsheet on our google drive *DARS* (with exeption of grade data saved as csv files on the computer for privacy reasons). We use the function `gsheet2tbl` to import them to `R Studio` as tibbles. We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.
## Setup
First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`. ` lists_brut` contains 4 columns, under which we find the `19` types of assessment, the `18` aims of the degree (AoD) of the degree, and  two columns containing binary vectors indicating which assessment types and AoD  we will consider when ploting the data[^1].
Then we create a list with this same columns, but instead of having binary vectors for the plots, we keep vectors of only the names of relevant assessments and AoDs for the plots (`Assessment_plot`adnd `AoD_plot` respectively). We also any imported emtpy cells.
```{r import list}
lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')
lists <- list(
  Assessment      = lists_brut$Assessment,
  Assessment_plot = lists_brut$Assessment[lists_brut$`Assessment for Plot` == 1],
  AoD             = lists_brut$Aim[!is.na(lists_brut$Aim)],
  AoD_plot        = lists_brut$Aim[lists_brut$`Aim for Plot`[!is.na(lists_brut$Aim)] == 1]
  )
rm(lists_brut)
```

@@

d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
  select(- `Comment on Assessment`) %>%
  gather(Assessment, assessment_covered, - Code, factor_key = T) %>%
  mutate(assessment_covered = as.logical(assessment_covered)) %>%
  filter(assessment_covered) %>%
  select(- assessment_covered) %>%
  arrange(Code)
print(d_assessment)

d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050') %>%
  select(- c(Comments, Comments_for_Jeroen)) %>%
  gather(AoD, AoD_covered, -c(Code, Objectives), factor_key = T) %>%
  mutate(AoD_covered = as.logical(AoD_covered)) %>%
  rename(ILO = Objectives) %>%
  filter(AoD_covered) %>%
  select(- AoD_covered) %>%
  arrange(Code)
print(d_ILO)
```

@@

In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
```{r d_AoD_ILO}
d_AoD_ILO <- d_ILO %>%
  distinct(Code, AoD)
print(d_AoD_ILO)
```

@@

```{r map_assessment_AoD}
map_assessment_AoD <- as.matrix(gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216')[,lists$AoD] %>%
                                  mutate_all(as.logical))
rownames(map_assessment_AoD) <- lists$Assessment
print(map_assessment_AoD[1:5, 8:12])
```

Now that we have the matrix `map_assessment_AoD`, we want to find out which AoDs are covered by a course through its assessments. To do this we create an empty tibble `d_AoD_assessment` to store which assessment is covered by each course, and which AoD said assessment covers.Then, we fill in the information with a loop.
In the loop, we first extract a row of `d_assessment` and save it as `observation`. Then, we determine the corresponding assessment which we save as `assessment`. Then, we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
```{r d_AoD_assessment}
d_AoD_assessment <- tibble(Code        = character(0),
                           Assessment  = character(0),
                           AoD         = character(0))
for(i in 1 : nrow(d_assessment)){

@@

Next, we keep ony one copy of each distinct combination of course and AoD in case a course had several assessments covering the same AoD (this is analogous to what we did with the tibble `d_AoD_ILO`).
```{r d_AoD_assessment distinct}
d_AoD_assessment <- d_AoD_assessment %>%
  distinct(Code, AoD)
print(d_AoD_assessment)
```

#### Combining AoD from ILOs and from assessments
Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `distinct` in case a course covers an AoD with both its ILOS and its assessments.
```{r rbind d_AoD_ILO and d_AoD_assessment}
d_AoD <- rbind(d_AoD_ILO,
               d_AoD_assessment) %>%
  distinct %>%
  arrange(Code)
rm(d_AoD_ILO, d_AoD_assessment)
print(d_AoD)
```

@@

Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. For this we create the following three tibbles:
1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
Then we use a `full_join` to add these variables to the tibble `d_course`.
```{r d_course detail}
d_ILO_detail <- d_ILO %>% 
  distinct(Code, ILO) %>%
  count(Code) %>%
  rename(n_ILO = n)

d_assessment_detail <- d_assessment %>%
  group_by(Code) %>%
  summarise(n_assessment = n(),
            `Assessments Covered` = paste(Assessment, collapse = ", "))

d_AoD_detail <- d_AoD %>%
  group_by(Code) %>%
  summarise(n_AoD = n(),
            `AoD Covered` = paste(AoD, collapse = ", "))

d_course_detail <- d_ILO_detail %>%
  full_join(d_assessment_detail, by = "Code") %>%
  full_join(d_AoD_detail       , by = "Code")

@@

```{r join d_course_detail}
d_course <- d_course %>%
  full_join(d_course_detail, by = "Code") %>%
  select(Code, `Course Title`, Cluster,
         n_ILO,
         n_assessment, `Assessments Covered`,
         n_AoD, `AoD Covered`, 
         everything())

@@

The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level). Yet, these course are also offered at the `2000` level (intermediate level). We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
```{r create UGR2000}
d_course <- d_course %>%
  rbind(filter(., Code %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
          mutate(Code = case_when(Code == "UGR3001" ~ "UGR2001",
                                  Code == "UGR3002" ~ "UGR2002",
                                  Code == "UGR3003" ~ "UGR2003",
                                  Code == "UGR3005" ~ "UGR2005")))
print(filter(d_course, Code %in% c("UGR2001", "UGR2002", "UGR2003", "UGR2005",
                                   "UGR3001", "UGR3002", "UGR3003", "UGR3005")))
```

Finally, we add a series of informative variable at the course level.
```{r d_course additional info}
d_course <- d_course %>%
  mutate(
    Letters = substring(Code, 1, 3),
    Number  = as.numeric(substring(Code, 4, 7)),
    Level   = case_when(between(Number, 1000, 1999) ~ "Introductory",
                        between(Number, 2000, 2999) ~ "Intermediate",
                        between(Number, 3000, 3999) ~ "Advanced"    ))

print(select(d_course, Code, Letters, Number, Level))
```

@@

```{r extracting overview, cache = TRUE}
# Setup
n_catalogue <- length(corpus_catalogues)
calendar_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
d_description <- tibble(Code            = character(0),
                        `Calendar Year` = character(0),
                        Overview        = character(0),
                        Description     = NA)

@@

    # Save overview
    Code <- substr(overview, start = 1, stop = 7)
    year <- calendar_years[n]
    d_description <- d_description %>%
      add_row(
        Code = Code,
        `Calendar Year` = year,
        Overview = overview,
        Description = NA
      )

@@

rm(corpus_catalogues,
   n_catalogue, calendar_years, course_code, content_to_exclude,
   n, cat,
   page_overview_start, page_overview_end,
   pages_to_exclude, cat_overview,
   first_three_letters, first_pages_overview,
   page, overview, Code, year)
print(d_description)
```

@@

  overview_by_line <- strsplit(x = toString(overview), split = symbol_to_line)[[1]]
  line_start    <- grep(pattern = start_descrip, x = overview_by_line) + 1
  line_end      <- grep(pattern = end_descrip  , x = overview_by_line) - 1
  # for overviews w/o Literature section, find section Instructional Format.
  if(is_empty(line_end)){
    line_end <- grep(pattern = "^Instructional format$", x = overview_by_line) - 1
    print(paste("line_end irregular for", d_description$Code[course],
                "in catalogue", d_description$`Calendar Year`[course]))
    } # close if-statement

@@

Since we want to use tools from dplyr and tidytext we must first transform our corpus into a dataframe.
```{r d_manual}
d_manual <- tidy(corpus_manuals) %>%
  select(id, text) %>%
  mutate(Code = substring(id, 1, 7)) %>%
  select(-id) %>%
  rename(Manual = text)
rm(corpus_manuals)
print(d_manual)
```

@@

To put everything into tidy text format, we first create three tibbles `d_overview_tidy`, `d_description_tidy`, `d_manual` that respectively store the overviews, descriptions and text from manuals in the tidy text format, with one row per course-year-word (and course-word for `d_manual`).
```{r tidy d_description}
d_overview <- d_description %>%
  select(Code, `Calendar Year`, Overview) %>%
  unnest_tokens(output = word, input = Overview)

d_description <- d_description %>%
  select(Code, `Calendar Year`, Description) %>%
  unnest_tokens(output = word, input = Description)

@@

dictionary <- select(d_overview, Code, word) %>%
  rbind(d_manual) %>% 
  distinct(word) %>%
  mutate(word_stem = purrr::map_chr(.x = word,
                                    .f = stem_hunspell))

@@

Our dataframe contains many variables and rows that are either empty or meaningless for our analysis. First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor"). Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
```{r}
d_transcript <- d_transcript %>%
  filter(`Appraisal (Description)` == "Grade supervisor", `Appraisal Type`=="7055") %>%
  select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
         `Program (Description)`, `Academic Year`, `Academic Session`,
         `Number rep. attemp`, `Grade symbol`, `Booking Status (Desc.)`) %>%
  rename(`Student ID Number` = `Student Number`,
         `Course Code` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         `Study Program` = `Program (Description)`,
         `Year_numerical` = `Academic Year`, # double check
         `Period` = `Academic Session`,
         `Number Repeated Attempt` = `Number rep. attemp`,
         Grade = `Grade symbol`,
         `Status` = `Booking Status (Desc.)`) %>% # is there a better name for the variable?
  distinct
```

Each faculty had a different code for their calendars, we want to standardise them so we can compare. We convert everything into UCM calendar codes (the correspondance between calendars was given to us by R. Vos) and save it under a variable `Period`. We also create another variable:
```{r}
d_transcript <- d_transcript %>%
  mutate(Period = case_when(Period == 1 ~ "1 to 6"  ,
                            Period == 2 ~ "1 to 3"  ,
                            Period == 3 ~ "4 to 6"  ,
                            Period == 680 ~ "5"     , # exception
                            Period == 350 ~ "3 to 5", # exception
                            Period == 403 ~ "4 to 5", # exception
                            Period == 900 ~ "1 to 6", # exception
                            between(Period, 100, 199) ~ "1",
                            between(Period, 200, 299) ~ "2",
                            between(Period, 300, 399) ~ "3",
                            between(Period, 400, 499) ~ "4",
                            between(Period, 500, 599) ~ "5",
                            between(Period, 600, 660) ~ "6",
                            between(Period, 901, 999) ~ "1")) %>%
  mutate(`Calendar Year`= paste(Year_numerical,Year_numerical+1, sep = "-"))
```

##Estimating concentrations:
For our analysis we would also like to know what the concentration of each student is. However, this is not given, so we will have to estimate. We know that the maximimum amount of courses a student can take outside of their concentration is 2. Therefore, if any student has more than two courses in one concetration, this should count towards the concentration. We expect students who addhere strictly to single concentrations, and then students who have a mixed concentration. However, it is possible that a person has not yet taken sufficient courses to make a call on their concentration, we will mark these people as "Undecided". Furthermore, it is possible that a student has taken too many courses out of all the concentrations, we will label these "Confused" and for all other cases we need to check the specifics, therefore we will label them "oops"

>>>>

# Import Data
The datasets we use are saved as spreadsheet on our google drive *DARS* (with exeption of grade data saved as csv files on the computer for privacy reasons). We use the function `gsheet2tbl` to import them to `R Studio` as tibbles. We use the tibble data format (an evolution of the data frame format) because this is the format of reference of the `tidyverse` on whose tools our analysis is heavily based.

## Setup
First, we import the spreadsheet with information pertraining the Aims of the Degree (AoD) and Assessments from the drive and save it under `lists_brut`. ` lists_brut` contains 4 columns, under which we find the `19` types of assessment, the `18` aims of the degree (AoD) of the degree, and  two columns containing binary vectors indicating which assessment types and AoD  we will consider when ploting the data[^1].
Then we create a list with this same columns, but instead of having binary vectors for the plots, we keep vectors of only the names of relevant assessments and AoDs for the plots (`Assessment_plot`adnd `AoD_plot` respectively). We also any imported emtpy cells.
```{r import list}
lists_brut <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1239912347')
lists <- list(
  Assessment      = lists_brut$Assessment,
  Assessment_plot = lists_brut$Assessment[lists_brut$`Assessment for Plot` == 1],
  AoD             = lists_brut$Aim[!is.na(lists_brut$Aim)],
  AoD_plot        = lists_brut$Aim[lists_brut$`Aim for Plot`[!is.na(lists_brut$Aim)] == 1]
  )
rm(lists_brut)
```

@@

d_assessment <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1102665750') %>%
  select(- `Comment on Assessment`) %>%
  gather(Assessment, assessment_covered, - `Course ID`, factor_key = T) %>%
  filter(assessment_covered == 1) %>%
  select(- assessment_covered) %>%
  arrange(`Course ID`)
print(d_assessment)

d_ILO <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=1896457050') %>%
  select(- c(Comments, Comments_for_Jeroen)) %>%
  gather(AoD, AoD_covered, -c(`Course ID`, Objectives), factor_key = T) %>%
  filter(AoD_covered == 1) %>%
  select(- AoD_covered) %>%
  rename(ILO = Objectives) %>%
  arrange(`Course ID`)
print(d_ILO)
```

@@

In order to determine which AoD each course covers with its ILOs, we first eliminate the AoD that are not covered by the ILOs, and then we keep only one instance of each combination of course and AoD in case a course had several ILOs covering the same AoD.
```{r d_AoD_ILO}
d_AoD_ILO <- distinct(d_ILO, `Course ID`, AoD)
print(d_AoD_ILO)
```

@@

```{r map_assessment_AoD}
map_assessment_AoD <- as.matrix(gsheet2tbl('https://docs.google.com/spreadsheets/d/1soRA1u5zf9oLNirGmZ9yZ7m2ccPa3XFemnxkj5AVRXo/edit#gid=719531216')[,lists$AoD] %>%
                                  mutate_all(as.logical))
rownames(map_assessment_AoD) <- lists$Assessment

# Print section of matrix
print(map_assessment_AoD[1:5, 8:12])
```

Now that we have the matrix `map_assessment_AoD`, we want to find out which AoDs are covered by a course through its assessments. To do this we create an empty tibble `d_AoD_assessment` to store which assessment is covered by each course, and which AoD said assessment covers.Then, we fill in the information with a loop.
In the loop, we first extract a row of `d_assessment` and save it as `observation`. Then, we determine the corresponding assessment which we save as `assessment`. Then, we use the matrix `map_assessment_AoD` to determine which AoD `assessment` covers and use `cbind` and `rbind` to add the information to the tibble `d_AoD_assessment`.
```{r d_AoD_assessment}
d_AoD_assessment <- tibble(`Course ID` = character(0),
                           Assessment  = character(0),
                           AoD         = character(0))

for(i in 1 : nrow(d_assessment)){

@@

Next, we keep ony one copy of each distinct combination of course and AoD in case a course had several assessments covering the same AoD (this is analogous to what we did with the tibble `d_AoD_ILO`).
```{r d_AoD_assessment distinct}
d_AoD_assessment <- distinct(d_AoD_assessment, `Course ID`, AoD)
print(d_AoD_assessment)
```

#### Combining AoD from ILOs and from assessments
Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `distinct` in case a course covers an AoD with both its ILOS and its assessments.
```{r rbind d_AoD_ILO and d_AoD_assessment}
d_AoD <- rbind(d_AoD_ILO,
               d_AoD_assessment) %>%
  distinct %>%
  arrange(`Course ID`)

rm(d_AoD_ILO, d_AoD_assessment)
print(d_AoD)
```

@@

Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. For this we create the following three tibbles:
1) `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains.
2) `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers. 
3) `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. 
Then we use a `full_join` to add these variables to the tibble `d_course`.
```{r d_course detail}
d_ILO_detail <- d_ILO %>% 
  distinct(`Course ID`, ILO) %>%
  count(`Course ID`) %>%
  rename(n_ILO = n)

d_assessment_detail <- d_assessment %>%
  group_by(`Course ID`) %>%
  summarise(n_assessment = n(),
            `Assessments Covered` = paste(Assessment, collapse = ", "))

d_AoD_detail <- d_AoD %>%
  group_by(`Course ID`) %>%
  summarise(n_AoD = n(),
            `AoD Covered` = paste(AoD, collapse = ", "))

d_course_detail <- d_ILO_detail %>%
  full_join(d_assessment_detail, by = "Course ID") %>%
  full_join(d_AoD_detail       , by = "Course ID")

@@

```{r join d_course_detail}
d_course <- d_course %>%
  full_join(d_course_detail, by = "Course ID") %>%
  select(`Course ID`, `Course Title`, Cluster,
         n_ILO,
         n_assessment, `Assessments Covered`,
         n_AoD, `AoD Covered`, 
         everything())

@@

The undegraduate research courses (*UGR-*) are only present at the `3000` level (advanced level). Yet, these course are also offered at the `2000` level (intermediate level). We use an `rbind` to duplicate the rows of the course `UGR3000` and mutate their `Code` to `UGR2000`.
```{r create UGR2000}
d_course <- d_course %>%
  rbind(filter(., `Course ID` %in% c("UGR3001", "UGR3002", "UGR3003", "UGR3005")) %>%
          mutate(`Course ID` = case_when(`Course ID` == "UGR3001" ~ "UGR2001",
                                  `Course ID` == "UGR3002" ~ "UGR2002",
                                  `Course ID` == "UGR3003" ~ "UGR2003",
                                  `Course ID` == "UGR3005" ~ "UGR2005")))

print(filter(d_course, `Course ID` %in% c("UGR2001", "UGR2002", "UGR2003", "UGR2005",
                                          "UGR3001", "UGR3002", "UGR3003", "UGR3005")))
```

Finally, we add a series of informative variable at the course level.
```{r d_course additional info}
d_course <- d_course %>%
  mutate(
    Letters = substring(`Course ID`, 1, 3),
    Number  = as.numeric(substring(`Course ID`, 4, 7)),
    Level   = case_when(between(Number, 1000, 1999) ~ "Introductory",
                        between(Number, 2000, 2999) ~ "Intermediate",
                        between(Number, 3000, 3999) ~ "Advanced"    ))

print(select(d_course, `Course ID`, Letters, Number, Level))
```

@@

```{r extracting overview, cache = TRUE}
# Setup
n_catalogue <- length(corpus_catalogues)
academic_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
d_description <- tibble(`Course ID`     = character(0),
                        `Academic Year` = character(0),
                        Overview        = character(0),
                        Description     = NA)

@@

    # Save overview
    code <- substr(overview, start = 1, stop = 7)
    year <- academic_years[n]
    d_description <- d_description %>%
      add_row(
        `Course ID` = code,
        `Academic Year` = year,
        Overview = overview,
        Description = NA
      )

@@

rm(corpus_catalogues,
   n_catalogue, academic_years, course_code, content_to_exclude,
   n, cat,
   page_overview_start, page_overview_end,
   pages_to_exclude, cat_overview,
   first_three_letters, first_pages_overview,
   page, overview, code, year)
print(d_description)
```

@@

  overview_by_line <- strsplit(x = toString(overview), split = symbol_to_line)[[1]]
  line_start    <- grep(pattern = start_descrip, x = overview_by_line) + 1
  line_end      <- grep(pattern = end_descrip  , x = overview_by_line) - 1
  # for overviews w/o Literature section, find section Instructional Format.
  if(is_empty(line_end)){
    line_end <- grep(pattern = "^Instructional format$", x = overview_by_line) - 1
    print(paste("line_end irregular for", d_description$`Course ID`[course],
                "in catalogue", d_description$`Calendar Year`[course]))
    } # close if-statement

@@

Since we want to use tools from dplyr and tidytext we must first transform our corpus into a dataframe.
```{r d_manual}
d_manual <- tidy(corpus_manuals) %>%
  select(id, text) %>%
  mutate(`Course ID` = substring(id, 1, 7)) %>%
  select(-id) %>%
  rename(Manual = text)

rm(corpus_manuals)
print(d_manual)
```

@@

To put everything into tidy text format, we first create three tibbles `d_overview_tidy`, `d_description_tidy`, `d_manual` that respectively store the overviews, descriptions and text from manuals in the tidy text format, with one row per course-year-word (and course-word for `d_manual`).
```{r tidy d_description}
d_overview <- d_description %>%
  select(`Course ID`, `Academic Year`, Overview) %>%
  unnest_tokens(output = word, input = Overview)

d_description <- d_description %>%
  select(`Course ID`, `Academic Year`, Description) %>%
  unnest_tokens(output = word, input = Description)

@@

dictionary <- select(d_overview, `Course ID`, word) %>%
  rbind(d_manual) %>% 
  distinct(word) %>%
  mutate(word_stem = purrr::map_chr(.x = word,
                                    .f = stem_hunspell))

@@

Our dataframe contains many variables and rows that are either empty or meaningless for our analysis. First, we filter, the final grades of studets to keep only relevant rows (Final Confirmed Grades are those with `Appraisal (Description)` as "Grade supervisor"). Then we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.
```{r}
d_transcript <- d_transcript %>%
  filter(`Appraisal (Description)` == "Grade supervisor", `Appraisal Type`=="7055") %>%
  select(`Student Number`,
         `Module (Abbrev.)`,
         `Module (Desc.)`,
         `Program (Description)`,
         `Academic Year`,
         `Academic Session`,
         `Number rep. attemp`,
         `Grade symbol`,
         `Booking Status (Desc.)`) %>%
  rename(`Student ID` = `Student Number`,
         `Course ID` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         `Study Program` = `Program (Description)`,
         Year_numerical = `Academic Year`, # double check
         Period = `Academic Session`,
         `Number Repeated Attempt` = `Number rep. attemp`,
         Grade = `Grade symbol`,
         Status = `Booking Status (Desc.)`) %>% # is there a better name for the variable?
#  mutate(as.POSIXct('2/5/2010',format='%m/%d/%Y')) %>%
  distinct
```

Each faculty had a different code for their calendars, we want to standardise them so we can compare. We convert everything into UCM calendar codes (the correspondance between calendars was given to us by R. Vos) and save it under a variable `Period`. We also create another variable:
```{r}
d_transcript <- d_transcript %>%
  mutate(Period = case_when(Period == 1 ~ "1 to 6"  ,
                            Period == 2 ~ "1 to 3"  ,
                            Period == 3 ~ "4 to 6"  ,
                            Period == 680 ~ "5"     , # exception
                            Period == 350 ~ "3 to 5", # exception
                            Period == 403 ~ "4 to 5", # exception
                            Period == 900 ~ "1 to 6", # exception
                            between(Period, 100, 199) ~ "1",
                            between(Period, 200, 299) ~ "2",
                            between(Period, 300, 399) ~ "3",
                            between(Period, 400, 499) ~ "4",
                            between(Period, 500, 599) ~ "5",
                            between(Period, 600, 660) ~ "6",
                            between(Period, 901, 999) ~ "1")) %>%
  mutate(`Academic Year`= paste(Year_numerical, Year_numerical + 1, sep = "-"))
```

## DO LATER (Estimating concentrations)
For our analysis we would also like to know what the concentration of each student is. However, this is not given, so we will have to estimate. We know that the maximimum amount of courses a student can take outside of their concentration is 2. Therefore, if any student has more than two courses in one concetration, this should count towards the concentration. We expect students who addhere strictly to single concentrations, and then students who have a mixed concentration. However, it is possible that a person has not yet taken sufficient courses to make a call on their concentration, we will mark these people as "Undecided". Furthermore, it is possible that a student has taken too many courses out of all the concentrations, we will label these "Confused" and for all other cases we need to check the specifics, therefore we will label them "oops"
